Tech United Eindhoven is the RoboCup student team of Eindhoven University of Technology that (since 2005) successfully competes in the robot soccer Middle Size League (MSL) and later (2011) joined the ambitious @Home League. The Tech United @Home team currently holds the runner up title of RoboCup 2016 in Leipzig and is the reigning European Champion. (2016 RoboCup European Open, Eindhoven)

Our ambition is to extend our team, efforts and expertise with a new winner: the Toyota Human Support Robot (HSR). This standard platform will enable us to further increase our impact on the robotics open source community.

We are driven by our personal believe that service robots will have an immensely positive impact on the quality of live and independence of people; especially elderly and physically impaired people can benefit from this ground-breaking technology. It is not only valuable technology, but also has urgency as most of the western economies have an aging society. We are therefore intrinsically motivated to contribute to the open source community to move this technology to new boundaries that allow robots to safely, robustly and effectively function and work around people. 

It is our firm believe that the impact, acceptance and use of new technology greatly depends on standardization of hardware and software systems. Metaphorically this is the foundation upon which great technology can be build and scaled. We see the availability of the HSR as a step forward in creating an eco-system that fosters new innovation and pushed the boundaries of what’s possible. 

This proposal will explain our development plans with the Toyota HSR system.